\documentclass{beamer} % Beamer document class for slides

%\usepackage{natbib} - natbib is not working in beamer

\usepackage[style=apa]{biblatex}
\addbibresource{references.bib}

\usetheme{Madrid} % Choose a theme

\title{Introduction to LaTeX} 
\author{Jakub Michańków} 
\date{\today} 

\begin{document}

\begin{frame} % Title frame
  \titlepage % Title page generated automatically based on \title, \author, and \date
\end{frame}

\begin{frame}{Outline} 
  \tableofcontents 
\end{frame}

\section{Introduction} % First section
\begin{frame}{Introduction} % Introduction frame
  \begin{itemize}
    \item LaTeX is a typesetting system.
    \item It is commonly used for technical and scientific documents.
    \item Beamer is a LaTeX document class for creating presentations.
  \end{itemize}
\end{frame}

\section{Basic Commands} % Second section
\begin{frame}{Basic Commands} % Basic Commands frame
  \begin{itemize}
    \item Use \textbackslash documentclass\{beamer\} to specify the document class.
    \item Choose a theme using \textbackslash usetheme\{\}.
    \item Create frames using the \textbackslash begin\{frame\} and \textbackslash end\{frame\} commands.
    \item And an example of citation \cite{einstein1905}
  \end{itemize}
\end{frame}

\section{Examples} % Third section
\begin{frame}{Examples} % Examples frame
  \begin{itemize}
    \item See previous examples for creating content such as text, equations, lists, figures, tables, references, and citations.
    \item These elements can be included in slides just like in regular LaTeX documents.
  \end{itemize}
\end{frame}

\section{Conclusion} % Fourth section
\begin{frame}{Conclusion} % Conclusion frame
  \begin{itemize}
    \item LaTeX and Beamer provide powerful tools for creating professional-looking presentations.
    \item Experiment with different themes and layouts to customize your slides.
    \item Practice creating slides to become more familiar with the process.
  \end{itemize}
\end{frame}


\section{References} 
\begin{frame}{References}
    \printbibliography
\end{frame}

\end{document}